### 2020-02-03 README.Rmd
hopefully

You can install the released version of eurobarometer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("eurobarometer")
```

And the development version from [GitHub](https://github.com/) with:

>>>>

At this moment yuo cannot install yest the packgae from [CRAN](https://CRAN.R-project.org), but there is a development version on [GitHub](https://github.com/):
